Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-10 tensor/draft/draft-tensor-op.tex
[tensor] Reformat draft to EPJC

\documentclass[prd,preprintnumbers,nofootinbib,twocolumn]{revtex4-1}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{multirow}
\usepackage{xcolor}

@@

% references to ...
\def \refeq#1{(\ref{#1})}
\def \refsec#1{sec.~\ref{#1}}
\def \refSec#1{Sec.~\ref{#1}}
\def \refapp#1{app.~\ref{#1}}
\def \reffig#1{fig.~\ref{#1}}
\def \reftab#1{tab.~\ref{#1}}

@@

%%
%% Comments
%%
\newcommand{\danny}[1]{{\color{purple}{#1}}}
\newcommand{\eos}[1]{{\color{red}{#1}}}   % things to be checked and replaced with EOS results
\newcommand{\fred}[1]{{\color{green}{#1}}}
\newcommand{\todo}[1]{{\color{blue}{ {\bf ToDo: }{#1}}}}
\newcommand{\checked}[1]{{\color{magenta}{ {\bf Checked: }{#1}}}}

@@

\title{Constraints on tensor and scalar couplings from
  $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$
}

\author{Frederik Beaujean}
\affiliation{
  C2PAP, Excellence Cluster Universe,\\
  Ludwig-Maximilians-Universit\"at M\"unchen,
  Garching, Germany
}

\author{Christoph Bobeth}
\affiliation{
  Institute for Advanced Study,
  Technische Universit\"at M\"unchen,
  Garching, Germany
}

\author{Stephan Jahn}
\affiliation{
  Max Planck institute for physics, Munich.\\
  Excellence Cluster Universe,
  Technische Universit\"at M\"unchen,
  Garching, Germany
}

\date{\today}

\preprint{EOS-2015-??, FLAVOUR(267104)-ERC-107}

@@

%
%
%

\maketitle

@@

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
  %\includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \caption{ The sensitivity to the tensor coupling
      $\wilson{T}$ of $F_H$ [first row] and ${\cal B}$ [second row] in
      $B^+ \to K^+ \bar\mu\mu$ and ${\cal B}$ [third row], $J_{1c} +
      J_{2c}$ [fourth row], and $J_{1s}-3 J_{2s}$ [fifth row] in $B^0 \to K^{*0}
      \bar\mu\mu$ integrated over low- and high-$q^2$ bins. In the
      last two rows, the observables are normalized by the lifetime of
      the $B$ meson for easier comparison with the branching
      ratios. The bands represent the theory uncertainties at 68\%
      and 95\% probability.  For comparison, two sets of bands are
      shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
      $\wilson[NP]{9} = -1.1$ (red), and an additional band of the
      latest 68\% uncertainty reported by LHCb (grey) if a measurement
      is available.
      }
  \label{fig:FHvsCT}
\end{figure*}

@@

\begin{table*}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccc}
\hline
Channel & Constraints & Kinematics & Source
\\
\hline \hline
$B_s\to \bar\mu\mu$
& $\int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
\\
\hline
\multirow{2}{*}{${B^+\to K^+ \bar\mu\mu}$}
    & \multirow{2}{*}{$\BR_\mu$}
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll} \\
    &
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014pli} \\
    & $A_{\rm FB}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa, CDF:2012:BKstarll} \\
    & $F_{H}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
    ${B^0\to K^{\ast 0} \bar\mu\mu}$
    & $\BR_\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm FB}^\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline \hline
${B\to K}$ form factors
    & $f_{0,+,T}$   &  $q^2 = 17,\, 20,\, 23$ GeV$^2$  & \cite{Bouchard:2013eph} \\
\hline
\multirow{2}{*}{${B\to K^*}$ {form factors}}
    & $V,\,A_{0,1,2},\, T_{1,2,3}$ &  $q^2 = 0.1,\, 4.1,\, 8.1,\, 12.1$ GeV$^2$  & \cite{Straub:2015ica} \\
    & $V,\,A_{0,1,2},\, T_{1,2,3}$
    & $q^2 \in [11.9,\, 17.8]$ GeV$^2$  & \cite{Horgan:2013hoa, Horgan:2015vla}  \\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:observables} List of all observables of the various
  $b\to s \bar\mu\mu$ decays that enter the fits with respective kinematics
  and experiments that provide the measurements. LCSR and lattice results of
  $B\to K^{(*)}$ form factors are used to constrain parameters of their
  $q^2$-dependence.
  For more details see the text and \refapp{app:theory:inputs}.
}
\end{center}
\end{table*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  \hline \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.32,\, 0.16]$ ($[-0.52,\, 0.35]$) $\quad$
  & $\quad$ $[-0.29,\, 0.09]$ ($[-0.43,\, 0.27]$) $\quad$
  & $\quad$ $[-0.23,\, 0.14]$ ($[-0.39,\, 0.30]$) $\quad$
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & $[-0.19,\, 0.21]$ ($[-0.37,\, 0.35]$)
  & $[-0.17,\, 0.22]$ ($[-0.33,\, 0.37]$)
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & $[-0.19,\, 0.17]$ ($[-0.33,\, 0.33]$)
  & $[-0.18,\, 0.16]$ ($[-0.32,\, 0.32]$)
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.24,\, 0.25]$ ($[-0.44,\, 0.45]$)
  & $[-0.21,\, 0.19]$ ($[-0.37,\, 0.35]$)
  & $[-0.20,\, 0.18]$ ($[-0.36,\, 0.35]$)
  \\
  \hline
  $|\wilson{T}|$, $|\wilson{T5}|$
  & $[0.13,\, 0.43]$ ($[0.03,\, 0.57]$)
  & $[0.09,\, 0.33]$ ($[0.02,\, 0.44]$)
  & $[0.10,\, 0.33]$ ($[0.02,\, 0.43]$)
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ --- [upper] 1D-marginalized
     at 68\% (95\%) probability and [lower] 2D-marginalized --- when using
     measurements of $i)$ only $F_H^\mu$, $ii)$ $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and $iii)$ allowing
     also complex-valud new physics contributions to $\wilson{9,\,10}$. \fred{For 9,10,S,P,T,T5, the absolute value is in $[0.077,0.269] ([0.020, 0.379])$}
  }
\end{table*}

@@

\begin{figure*}
  \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_0,2}
%  \includegraphics[width=.32\textwidth]{plots/pdf/scSP_Bsmumu,scSP_FH,sc910SP_K_KstarBR_Bsmumu_4,6}
  \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,sc910SP_K_KstarBR_Bsmumu_0,4}
  \includegraphics[width=.325\textwidth]{plots/pdf/scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_2,6}
  \caption{
    The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$
    from $i)$ only $F_H^\mu$~(grey dotted), $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$
    (blue dashed) and $iii)$ their combination with other data in \reftab{tab:observables}
    as well as non-zero $\wilson[]{9,\,9',\,10,\, 10'}$ (red solid)
    at 68\% (darker) and 95\% (lighter) probability. The constraints on
    Re$(\wilson{P}Ê\pm \wilson{P'})$ are identical to Re$(\wilson{S}Ê\pm \wilson{S'})$,
    apart from a small shift of the contours by $(+0.2,\, +0.15)$. The SM is indicated
    by the black diamond.
  }
  \label{fig:scalar}
\end{figure*}

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
%\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & only $\overline{\cal B}(B_s \to \bar\mu\mu)$
  & all
  \\
  set of couplings
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P',\,9,\,9',\,10,\,10'}$
  \\
  \hline \hline
  $\mbox{Re}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & $\quad$ $[-0.10,\, 0.08]$ ($[-0.14,\, 0.13]$) $\quad$
  & $\quad$ $[-0.08,\, 0.07]$ ($[-0.13,\, 0.13]$) $\quad$
  \\
  $\mbox{Im}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & $\quad$ $[-0.07,\, 0.07]$ ($[-0.11,\, 0.12]$) $\quad$
  & $\quad$ $[-0.07,\, 0.07]$ ($[-0.12,\, 0.11]$) $\quad$
  \\[0.1cm]
  $\mbox{Re}(\wilson{S} + \wilson{S'})$
  & $[-0.36,\, 0.39]$ ($[-0.69,\, 0.68]$)
  & $-$
  & $[-0.32,\, 0.32]$ ($[-0.59,\, 0.62]$)
  \\
  $\mbox{Im}(\wilson{S} + \wilson{S'})$
  & $[-0.37,\, 0.35]$ ($[-0.68,\, 0.66]$)
  & $-$
  & $[-0.25,\, 0.41]$ ($[-0.57,\, 0.64]$)
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} - \wilson{P'})$
  & $-$
  & $[ 0.05,\, 0.20]$ ($[ 0.01,\, 0.26]$)
  & $[ 0.00,\, 0.16]$ ($[-0.07,\, 0.22]$)
  \\
  $\mbox{Im}(\wilson{P} - \wilson{P'})$
  & $-$
  & $[-0.07,\, 0.08]$ ($[-0.12,\, 0.12]$)
  & $[-0.07,\, 0.09]$ ($[-0.14,\, 0.16]$)
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} + \wilson{P'})$
  & $[-0.24,\, 0.51]$ ($[-0.51,\, 0.82]$)
  & $-$
  & $[-0.12,\, 0.52]$ ($[-0.42,\, 0.78]$)
  \\
  $\mbox{Im}(\wilson{P} + \wilson{P'})$
  & $[-0.36,\, 0.37]$ ($[-0.67,\, 0.67]$)
  & $-$
  & $[-0.37,\, 0.29]$ ($[-0.68,\, 0.57]$)
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cSP:1-dimCLs}
     The 1D-marginalized constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$
     at 68\% (95\%) probability from measurements of $i)$ only $F_H^\mu$,
     $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $iii)$ all the data in
     \reftab{tab:observables} and additional new physics contributions to
     $\wilson{9,\, 9',\, 10,\,10'}$.
  }
\end{table*}

@@

\begin{figure*}
  \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_0,2}
  \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_1,3}
  \caption{
    Constraints (2D-marginalized) on complex-valued scalar couplings
    $\wilson{S,\,S'}$ in the scenario SM-EFT from all data in
    \reftab{tab:observables} (red) at 68\% (darker) and 95\%
    (lighter) probability when marginalising over non-zero $\mbox{Re, Im}
    (\wilson[NP]{10,\,10'}) \in [-7,\,7]$.
    For comparison the according constraints from only $\overline{\cal B}(B_s\to \bar\mu\mu)$
    and $F_H^\mu$ \todo{What else?}
    (dashed blue contours) at 68\% (inner) and 95\% (outer) probability.
    The SM is indicated by the black diamond.
  }
  \label{fig:scalar:SM-EFT}
\end{figure*}

@@

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\begin{acknowledgments}
  We are grateful to Danny van Dyk for helpful discussions and his support on
  EOS \cite{EOS}. Concerning form factor results from lattice, we thank Chris
  Bouchard and Matthew Wingate for communications on their results of $B\to K$
  \cite{Bouchard:2013eph} and $B\to K^*$ \cite{Horgan:2015vla} form factors,
  respectively. We thank also David Straub for his support with LCSR results of
  $B\to K^*$ form factors \cite{Straub:2015ica}.
  C.B. was supported by the ERC Advanced Grant project ``FLAVOUR''
  (267104).
\end{acknowledgments}

>>>>

% \documentclass[prd,preprintnumbers,nofootinbib,twocolumn]{revtex4-1}
\documentclass[twocolumn,epjc3]{svjour3}

\RequirePackage[T1]{fontenc}
\RequirePackage{mathptmx}      % use Times fonts if available on your TeX system
\RequirePackage{flushend}
\RequirePackage[numbers,sort&compress]{natbib}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue,linkcolor=blue]{hyperref}

\journalname{Eur. Phys. J. C}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{multirow}
\usepackage{xcolor}

@@

% references to ...
\def \refeq#1{(\ref{#1})}
\def \refsec#1{Section \ref{#1}}
\def \refapp#1{\ref{#1}}
\def \reffig#1{Figure \ref{#1}}
\def \reftab#1{Table \ref{#1}}

@@

%%
%% Comments
%%
\newcommand{\eos}[1]{{\color{red}{#1}}}   % things to be checked and replaced with EOS results
\newcommand{\fred}[1]{{\color{green}{#1}}}
\newcommand{\todo}[1]{{\color{purple}{ {\bf ToDo: }{#1}}}}
\newcommand{\checked}[1]{{\color{magenta}{ {\bf Checked: }{#1}}}}

@@

% better line breaks, http://tex.stackexchange.com/questions/32062
\sloppy

\title{Constraints on tensor and scalar couplings from
  $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$
}
\author{Frederik Beaujean\thanksref{e1,addr1}
  \and
  Christoph Bobeth\thanksref{e2,addr2}
  \and
  Stephan Jahn\thanksref{e3,addr3,addr4}
}
\institute{
  C2PAP, Excellence Cluster Universe,
  Ludwig-Maximilians-Universit\"at M\"unchen,
  Garching, Germany\label{addr1}
  \and
  Institute for Advanced Study,
  Technische Universit\"at M\"unchen,
  Garching, Germany\label{addr2}
  \and
  Excellence Cluster Universe,
  Technische Universit\"at M\"unchen,
  Garching, Germany\label{addr3}
  \and
  \emph{Present Address:}
  Max Planck institute for physics, Munich, Germany\label{addr4}
}

\thankstext[$\star$]{t1}{\todo{EOS-2015-??}, FLAVOUR(267104)-ERC-107}
\thankstext{e1}{e-mail: frederik.beaujean@lmu.de}
\thankstext{e2}{e-mail: christoph.bobeth@ph.tum.de}
\thankstext{e3}{e-mail: sjahn@mpp.mpg.de}

\date{\today}
\maketitle

@@

@@

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \begin{center}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
    % \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \end{center}
\caption{ The sensitivity to the tensor coupling
      $\wilson{T}$ of $F_H$ [first row] and ${\cal B}$ [second row] in
      $B^+ \to K^+ \bar\mu\mu$ and ${\cal B}$ [third row], $J_{1c} +
      J_{2c}$ [fourth row], and $J_{1s}-3 J_{2s}$ [fifth row] in $B^0 \to K^{*0}
      \bar\mu\mu$ integrated over low- and high-$q^2$ bins. In the
      last two rows, the observables are normalized by the lifetime of
      the $B$ meson for easier comparison with the branching
      ratios. The bands represent the theory uncertainties at 68\%
      and 95\% probability.  For comparison, two sets of bands are
      shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
      $\wilson[NP]{9} = -1.1$ (red), and an additional band of the
      latest 68\% uncertainty reported by LHCb (grey) if a measurement
      is available.
      }
  \label{fig:FHvsCT}
\end{figure*}

@@

\begin{table*}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccc}
\hline
Channel & Constraints & Kinematics & Source
\\
\hline \hline
$B_s\to \bar\mu\mu$
& $\int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
\\
\hline
\multirow{2}{*}{${B^+\to K^+ \bar\mu\mu}$}
    & \multirow{2}{*}{$\BR_\mu$}
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll} \\
    &
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014pli} \\
    & $A_{\rm FB}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa, CDF:2012:BKstarll} \\
    & $F_{H}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
    ${B^0\to K^{\ast 0} \bar\mu\mu}$
    & $\BR_\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm FB}^\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
${B\to K}$ form factors
    & $f_{0,+,T}$   &  $q^2 = 17,\, 20,\, 23$ GeV$^2$  & \cite{Bouchard:2013eph} \\
\hline
\multirow{2}{*}{${B\to K^*}$ {form factors}}
    & $V,\,A_{0,1,2},\, T_{1,2,3}$ &  $q^2 = 0.1,\, 4.1,\, 8.1,\, 12.1$ GeV$^2$  & \cite{Straub:2015ica} \\
    & $V,\,A_{0,1,2},\, T_{1,2,3}$
    & $q^2 \in [11.9,\, 17.8]$ GeV$^2$  & \cite{Horgan:2013hoa, Horgan:2015vla}  \\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:observables} List of all observables of the various
  $b\to s \bar\mu\mu$ decays that enter the fits with respective kinematics
  and experiments that provide the measurements. LCSR and lattice results of
  $B\to K^{(*)}$ form factors are used to constrain parameters of their
  $q^2$-dependence.
  For more details see the text and \refapp{app:theory:inputs}.
}
\end{center}
\end{table*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  \begin{center}
  \begin{tabular}{cccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.32,\, 0.16]$ ($[-0.52,\, 0.35]$) $\quad$
  & $\quad$ $[-0.29,\, 0.09]$ ($[-0.43,\, 0.27]$) $\quad$
  & $\quad$ $[-0.23,\, 0.14]$ ($[-0.39,\, 0.30]$) $\quad$
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & $[-0.19,\, 0.21]$ ($[-0.37,\, 0.35]$)
  & $[-0.17,\, 0.22]$ ($[-0.33,\, 0.37]$)
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & $[-0.19,\, 0.17]$ ($[-0.33,\, 0.33]$)
  & $[-0.18,\, 0.16]$ ($[-0.32,\, 0.32]$)
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.24,\, 0.25]$ ($[-0.44,\, 0.45]$)
  & $[-0.21,\, 0.19]$ ($[-0.37,\, 0.35]$)
  & $[-0.20,\, 0.18]$ ($[-0.36,\, 0.35]$)
  \\
  \hline
  $|\wilson{T}|$, $|\wilson{T5}|$
  & $[0.13,\, 0.43]$ ($[0.03,\, 0.57]$)
  & $[0.09,\, 0.33]$ ($[0.02,\, 0.44]$)
  & $[0.10,\, 0.33]$ ($[0.02,\, 0.43]$)
  \\
  \hline
  \end{tabular}

  \end{center}

  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ --- [upper] 1D-marginalized
     at 68\% (95\%) probability and [lower] 2D-marginalized --- when using
     measurements of $i)$ only $F_H^\mu$, $ii)$ $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and $iii)$ allowing
     also complex-valud new physics contributions to $\wilson{9,\,10}$. \fred{For 9,10,S,P,T,T5, the absolute value is in $[0.077,0.269] ([0.020, 0.379])$}
  }
\end{table*}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_0,2}
    % \includegraphics[width=.32\textwidth]{plots/pdf/scSP_Bsmumu,scSP_FH,sc910SP_K_KstarBR_Bsmumu_4,6}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,sc910SP_K_KstarBR_Bsmumu_0,4}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_2,6}
  \end{center}
  \caption{
    The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$
    from $i)$ only $F_H^\mu$~(grey dotted), $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$
    (blue dashed) and $iii)$ their combination with other data in \reftab{tab:observables}
    as well as non-zero $\wilson[]{9,\,9',\,10,\, 10'}$ (red solid)
    at 68\% (darker) and 95\% (lighter) probability. The constraints on
    Re$(\wilson{P}Ê\pm \wilson{P'})$ are identical to Re$(\wilson{S}Ê\pm \wilson{S'})$,
    apart from a small shift of the contours by $(+0.2,\, +0.15)$. The SM is indicated
    by the black diamond.
  }
  \label{fig:scalar}
\end{figure*}

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  \begin{center}
  \begin{tabular}{cccc}
  \hline
  data set
  & only $F_H^\mu$
  & only $\overline{\cal B}(B_s \to \bar\mu\mu)$
  & all
  \\
  set of couplings
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P',\,9,\,9',\,10,\,10'}$
  \\
  \hline
  $\mbox{Re}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & $\quad$ $[-0.10,\, 0.08]$ ($[-0.14,\, 0.13]$) $\quad$
  & $\quad$ $[-0.08,\, 0.07]$ ($[-0.13,\, 0.13]$) $\quad$
  \\
  $\mbox{Im}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & $\quad$ $[-0.07,\, 0.07]$ ($[-0.11,\, 0.12]$) $\quad$
  & $\quad$ $[-0.07,\, 0.07]$ ($[-0.12,\, 0.11]$) $\quad$
  \\[0.1cm]
  $\mbox{Re}(\wilson{S} + \wilson{S'})$
  & $[-0.36,\, 0.39]$ ($[-0.69,\, 0.68]$)
  & $-$
  & $[-0.32,\, 0.32]$ ($[-0.59,\, 0.62]$)
  \\
  $\mbox{Im}(\wilson{S} + \wilson{S'})$
  & $[-0.37,\, 0.35]$ ($[-0.68,\, 0.66]$)
  & $-$
  & $[-0.25,\, 0.41]$ ($[-0.57,\, 0.64]$)
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} - \wilson{P'})$
  & $-$
  & $[ 0.05,\, 0.20]$ ($[ 0.01,\, 0.26]$)
  & $[ 0.00,\, 0.16]$ ($[-0.07,\, 0.22]$)
  \\
  $\mbox{Im}(\wilson{P} - \wilson{P'})$
  & $-$
  & $[-0.07,\, 0.08]$ ($[-0.12,\, 0.12]$)
  & $[-0.07,\, 0.09]$ ($[-0.14,\, 0.16]$)
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} + \wilson{P'})$
  & $[-0.24,\, 0.51]$ ($[-0.51,\, 0.82]$)
  & $-$
  & $[-0.12,\, 0.52]$ ($[-0.42,\, 0.78]$)
  \\
  $\mbox{Im}(\wilson{P} + \wilson{P'})$
  & $[-0.36,\, 0.37]$ ($[-0.67,\, 0.67]$)
  & $-$
  & $[-0.37,\, 0.29]$ ($[-0.68,\, 0.57]$)
  \\
  \hline
  \end{tabular}
  \end{center}

  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cSP:1-dimCLs}
     The 1D-marginalized constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$
     at 68\% (95\%) probability from measurements of $i)$ only $F_H^\mu$,
     $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $iii)$ all the data in
     \reftab{tab:observables} and additional new physics contributions to
     $\wilson{9,\, 9',\, 10,\,10'}$.
  }
\end{table*}

@@

\begin{figure*}
  \begin{center}
      \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_0,2}
      \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_1,3}
    \end{center}
    \caption{
    Constraints (2D-marginalized) on complex-valued scalar couplings
    $\wilson{S,\,S'}$ in the scenario SM-EFT from all data in
    \reftab{tab:observables} (red) at 68\% (darker) and 95\%
    (lighter) probability when marginalising over non-zero $\mbox{Re, Im}
    (\wilson[NP]{10,\,10'}) \in [-7,\,7]$.
    For comparison the according constraints from only $\overline{\cal B}(B_s\to \bar\mu\mu)$
    and $F_H^\mu$ \todo{What else?}
    (dashed blue contours) at 68\% (inner) and 95\% (outer) probability.
    The SM is indicated by the black diamond.
  }
  \label{fig:scalar:SM-EFT}
\end{figure*}

@@

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\begin{acknowledgements}
  We are grateful to Danny van Dyk for helpful discussions and his support on
  EOS \cite{EOS}. Concerning form factor results from lattice, we thank Chris
  Bouchard and Matthew Wingate for communications on their results of $B\to K$
  \cite{Bouchard:2013eph} and $B\to K^*$ \cite{Horgan:2015vla} form factors,
  respectively. We thank also David Straub for his support with LCSR results of
  $B\to K^*$ form factors \cite{Straub:2015ica}.
  C.B. was supported by the ERC Advanced Grant project ``FLAVOUR''
  (267104).
\end{acknowledgements}
